\mytitle

### 2012-03-23 papers/SAS2012/implicitization.tex
Deux typos

\begin{compactenum}
	\item The starting subgraph is depicted on Figure
		\ref{fig:example-graph} Step 1. At the beginning, this graph has no
		transitions.
	\item
		We compute the new feasible paths that have to be added into the
		subgraph. We first find the path from $p_1$ to $p_3$ and obtain at $p_3$
		$\lstinline|x_old| = 0$. We then find the path

@@

		Finally, since the abstract value associated to $p_8$ is  
		$-10 \leq \lstinline|x_old| \leq 10$, the path from $p_8$ to $p_1$ is
		feasible and is added into $P$. The final subgraph is depicted on Figure
		\ref{fig:example-graph} Step 2.

>>>>

\begin{compactenum}
	\item The starting subgraph is depicted on Figure
		\ref{fig:example-graph} Step 1. At the beginning, this graph has no
		transitions.
	\item
		We compute the new feasible paths that have to be added into the
		subgraph. We first find the path from $p_1$ to $p_3$ and obtain at $p_3$
		$\lstinline|x_old| = 0$.
                \MM{TODO: il y avait cette phrase pas finie `` We then
                  find the path''. J'ai enlevé. C'est bon ?}

@@

		Finally, since the abstract value associated to $p_8$ is  
		$-10 \leq \lstinline|x_old| \leq 10$, the path from
                $p_8$ to $p_3$\MM{TODO: y'avait $p_1$ ici, j'ai mis $p_3$, c'est bon ?} is
		feasible and is added into $P$. The final subgraph is depicted on Figure
		\ref{fig:example-graph} Step 2.
